---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 8"
author: "Anikate Ganju"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 1 Exercises: 8.1, 8.2, 8.3

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(ggplot2)
library(mosaicData)
data(CPS85)
View(CPS85)
```

8.1
1)geom_point(): add a layer of glyphs
2)geom_histogram(): add a layer of glyphs
3)ggplot(): construct a graphics frame
4)scale_y_log10(): change the scale for the frame
5)ylab(): set an axis label
6)facet_wrap(): divide the frame into facets
7)geom_segment(): add a layer of glyphs
8)xlim(): change the scale for the frame
9)facet_grid(): divide the frame into facets

8.2
A)
```{r}
CPS85 %>%
  ggplot(aes(x=wage)) +
  facet_wrap(.~married) +
  geom_density(aes(color=sex, fill=sex),alpha=0.5) +
  xlim(c(0,30)) +
  theme_bw()
```

B)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  facet_wrap(.~married,nrow=2) +
  geom_smooth(aes(shape=sex, color=sex)) +
  theme_bw()
```

C)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  facet_wrap(~sector) +
  geom_smooth(aes(shape=sex, color=sex)) +
  ylim(c(0,25)) +
  theme_bw()
```

8.3
A)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  geom_point()
```
B)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  geom_point(aes(shape=sex)) +
  theme(legend.position="top")
```
C)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  facet_wrap(~married,nrow=2) +
  geom_point(aes(shape=sex)) +
  theme(legend.position="top")
```
D)
```{r}
CPS85 %>%
  ggplot(aes(x=age,y=wage)) +
  geom_point(aes(shape=married)) +
  ylim(c(0,32))
  theme(legend.position = "top")
```
