---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 15"
author: "Anikate Ganju"
output: html_notebook
---

## Assigned Exercises

- DC Ch 12 Exercises: 15.1-15.5
## Front Matter
```{r}
library(tidyverse)
library(mosaic)
library(DataComputing)
library(ggplot2)
library(lubridate)
```

## 15.1
```{r}
CPS85 %>%
 ggplot(aes(x = sex, y = wage )) +
 geom_boxplot(aes(fill = sex))
```
## 15.2
1) ~1.65 meters
2) Women: 1.6, Men: 1.75
3) 40yrsold: 26.25, 70yrsold: 27.5

## 15.3
```{r}
CPS85 %>%
  ggplot(aes(x = educ , y = wage, color = sex )) +
  geom_point((aes(fill = sex)))+
  stat_smooth(method = lm) + theme_bw() +
  ylim(0,15)
```

## 15.4
```{r}
Galton %>%
  ggplot(aes(x = mother , y = height, z=father)) +
  geom_contour() +
  facet_wrap(vars(sex))
```

## 15.5
1) No, the data does not indicate that ZIP codes with high elderly populations tend to have high child populations.
2) It is very possible for there to be no relation because I do not see any evidence of correlation within the points.

1)Computationally, the  blue line might be the 'line of best fit', but the data points are too spread out to make that line a good representation of the data spread
2)The height of the graph with 80 points has a height(in the middle) which is about half of the one with 20 points.
3)My calculations could be incorrect, but this does not make sense according to this graph, because with n=80, the width is still about 5 units wide. Which is no where close to 1/root(80).

