---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 11"
author: "Anikate Ganju"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 1 Exercises: 11.1, 11.2, 11.6

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)

data(ZipGeography)
```



## Chapter 11 Exercises

### Problem 11.1
The left_join, inner_join, and full_join data verbs require data as a paramenter because the function's purpose in itself is to join parts of data tables. Without a data table, we would get an error for no parameters given.

### Problem 11.2
There is no identifiers in either table for the data to match correctly.

### Problem 11.6
1)1910 rows, meaning 1910 different counties
```{r}
ZipGeography %>%
  group_by(County) %>%
  summarise(count=n())
View(ZipGeography)
```
2)Which city names are used in the most states? Find most recurring city name.
Abington recurred 193 times, which is the most used city name in the state.
```{r}
City <- ZipGeography %>%
  filter(!is.na(CityName)) %>%
  group_by(CityName) %>%
  summarise(Unique_States=n_distinct(State)) %>%
  filter(CityName!=" ") %>%
  arrange(desc(Unique_States))
View(City)
```
3)Identify cities that include more than 5% of their state population; which of those city names are used in the most states?

```{r}
fiveperc <- ZipGeography
fiveperc %>%
  
  group_by(State, CityName, population) %>%
  filter(HousingUnits>(0.05*population))
```
4)Does any state have more than one time zone? Yes, Alaska, Oregon, Hawaii, Idaho, Texas,
 Nebraska, Kansas, South Dakota, North Dakota, Michigan, Indiana, Kentucky, Tennesse, and Florida.
```{r}
diff_tz <- ZipGeography %>%
  filter(Timezone!=" ",State!="") %>%
  group_by(State, Timezone) %>%
  summarise(count=n())

View(diff_tz)
```
5)Does any city have more than one time zone?
Yes, every repeated case in the following dataframe is a city with more than one time zone. Ex: Acton
```{r}
diff_citytz <- ZipGeography %>%
  filter(Timezone!=" ",CityName!="") %>%
  group_by(CityName, Timezone) %>%
  summarise(count=n())

View(diff_citytz)
```
6)Does any county have more than one time zone?
Yes, every repeated case in the following dataframe is a county with more than one time zone. Ex: Suffolk
```{r}
diff_countytz <- ZipGeography %>%
  filter(Timezone != " ", County != "") %>%
  select(County,Timezone)

View(diff_countytz)
```