---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 11"
author: "Anikate Ganju"
output: html_notebook
---

## Assigned Exercises

- DC Chapter 1 Exercises: 11.1, 11.2, 11.6

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(DataComputing)

data(ZipGeography)
```



## Chapter 11 Exercises

### Problem 11.1
The left_join, inner_join, and full_join data verbs require data as a paramenter because the function's purpose in itself is to join parts of data tables. Without a data table, we would get an error for no parameters given.

### Problem 11.2
There is no identifiers in either table for the data to match correctly.

### Problem 11.6
1)1910 rows, meaning 1910 different counties
```{r}
ZipGeography %>%
  group_by(County) %>%
  summarise(count=n())
```
2)Which city names are used in the most states? Find most recurring city name.
Abington recurred 193 times, which is the most used city name in the state.
```{r}
ZipGeography %>%
  group_by(CityName) %>%
  summarise(count=n())
```
3)Identify cities that include more than 5% of their state population; which of those city names are used in the most states?

```{r}
ZipGeography %>%
  group_by(CityName) %>%
  filter(HousingUnits>(0.05*population))
```

