---
title: "MPG comparison"
author: "Anikate Ganju"
date: "11/17/2020"
output: html_notebook
---

Guiding Question: What type of cars give the best gas mileage?

Challenges encountered: disecting mpg given unorthodo dataset.

Visualization: # doors vs mpg. type of cars avg mpg(compact, SUV, etc.)



## Data Sources
Primary dataset: Auto-mpg data: https://www.kaggle.com/uciml/autompg-dataset
Secondary dataset: ggplot2::mpg

## Data Access
```{r}
library(ggplot2)
library(mosaicData)
library(dplyr)
library(tidyverse)
data(mpg)
```
Kaggle dataset access:
```{r}
kaggle_mpg <- read.csv("auto_mpg.csv")
glimpse(kaggle_mpg)
```
```{r}
head(kaggle_mpg)
```
```{r}
tail(kaggle_mpg)
```
ggplot mpg dataset access:
```{r}
gg_mpg <- (ggplot2::mpg)
glimpse(gg_mpg)
```
```{r}
head(gg_mpg)
```
```{r}
tail(gg_mpg)
```
## Data Wrangling
```{r}
mpg_drv_summary <- function() {
  ggplot(ggplot2::mpg) + 
    geom_bar(aes(x = cty)) +
    ggtitle("Spread of ggplot::mpg") +
    coord_flip()
}
```

```{r}
kaggle_mpg %>%
  filter(grepl("honda", car.name, ignore.case = TRUE)) %>%
  filter(mpg>32) %>%
  arrange(desc(mpg))
```
```{r}
honda_combmpg <-  
  gg_mpg %>%
  filter(grepl("honda", manufacturer, ignore.case = TRUE)) %>%
  mutate(comb_mpg=((cty+hwy)/2)) %>%
  arrange(desc(comb_mpg))

View(honda_combmpg)
```

```{r}
vw_combmpg <-  
  gg_mpg %>%
  filter(grepl("volkswagen", manufacturer, ignore.case = TRUE)) %>%
  mutate(comb_mpg=((cty+hwy)/2)) %>%
  arrange(desc(comb_mpg))

vw_combmpg %>%
  spread(key=cyl,value=comb_mpg)
```


## Data visualization
```{r}
vw_combmpg %>%
  ggplot(aes(x=displ,y=comb_mpg)) +
  geom_point() +
  aes(color=trans)
```

```{r}
honda_combmpg %>%
  ggplot(aes(x=displ,y=comb_mpg)) +
  geom_point() +
  aes(color=trans)
```
```{r}
mpg %>%
  ggplot(aes(x=cty)) +
  geom_density(aes(color=cty, fill=cty)) +
  xlim(c(0,30)) +
  theme_bw()
```

```{r}
mpg %>%
  ggplot(aes(x=cty,y=hwy)) +
  geom_point(aes(shape=manufacturer)) +
  theme(legend.position="top")
```

```{r}
mpg_drv_summary()
```
most cars from our ggplot dataset lie in the 10mpg to 20mpg range.
This is purely to show the spread of mpg in the city, of the cars in our dataset.

```{r}
col_summary <- function(df, col) {
  ggplot(df) +
    ggtitle("Spread of Volkswagen combined mpg") +
    geom_bar(aes(x={{col}})) + 
    coord_flip()
}

col_summary(vw_combmpg, comb_mpg)

```