---
title: "STAT 184 Homework Exercises" 
subtitle: "DataComputing Chapters 5 & 6"
author: "Anikate Ganju"
output: html_notebook
---
#togit

## Assigned Exercises

- DC Chapter 5 Exercises: 5.1
- DC Chapter 6 Exercises: 6.1,6.2,6.3,6.4,6.5,6.6,6.7,6.8,6.9,6.10

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())

# all packages used for the assignment
library(mosaic)
library(tidyverse)
library(ggplot2)
library(mosaicData)
library(DataComputing)
```


## 5.1
```{r}
ggplot(data=CPS85,aes(x=sex,y=wage ,fill=married)) +
  geom_bar(stat='identity',position='dodge') +
  facet_wrap(~race,ncol=3)
```

## 6.1
1)“1433B”, “1433E”, “1433G” and “1433Z”
2)no
3)Vertical Highest/lowest bars, red line to show general curve, and the asterik.

## 6.2
1)
x-axis: genes
y-axis: concentration of gene
Flux legend: shows whether flux is 0 or greater than 1
molecule legend: shows molecule by color
target receptors(bars on top): molecules grouped by receptor
2)
color: molecule type
fill: flux quantity
position: gene, concentration, and receptors
3)concentration and gene
4)gene and target

## 6.3
1)
black line: the label is the protein name, the color is polarity, and the size is determined by highest/lowest
asterik:represents signif
2)
center and signif define frame.
Horizontal: proteins
vertical: log2 ratio
3)yes
4)y-axis and the blue text

## 6.4
1)time-transportation arrival times
2)color maps the type of transportation and size of colored bars: duration of trip
3)transportation times is encodede by shape/style; position encodes eta
4)bus,train, labels, color of bar graph

## 6.5
B. State and Polling Organization.

## 6.6
C. Glyph: Rectangle. Graphical attribute: color.

## 6.7
D. NYT poll probability for the Democratic candidate.

## 6.8
A. Vertical scale: Name of state.
B. Vertical scale: Name of candidate.

## 6.9
```{r}
Small <- 
  NCHS %>%
  sample_n(size=5000)

Small %>%
  ggplot(aes(x=bmi,y=weight)) +
  geom_point() +
  aes(color=smoker)
```

## 6.10
a)layers of different Bacteria, viruses, archea, and eukaryotes
b)There is no scale, I believe.
